Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of two new
sources, which we did not observe before. These sources are
highlighted with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications. The source ``Error Message Mismatch''
indicates that \Mar{por favor, explique. nao consigo lembrar.}
\Igor{existem testes que realizam a comparacao de strings, o fuzzer pode
alterar o corpo da mensagem. Esta era a ideia, mas 
}

>>>>

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of two new
sources, which we did not observe before. These sources are
highlighted with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications. The source ``Error Message Mismatch''
indicates that \Mar{por favor, explique. nao consigo lembrar.}
\Igor{existem testes que realizam a comparacao de strings, o fuzzer pode
alterar o corpo da mensagem. Esta era a ideia, mas 
casos onde o fuzzer muda a msg em uma assercao 
(por exempo 'assertThrows(SyntaxError(), "SyntaxError: syntax error")') 
todos os engenhos falham e o teste nao ser reportado caso alcance esse bloco.
Porem, existem casos em que o teste falha por message mismatch, 
mas a discrepancia ocorre no engenho que nao exibe essa mensagem. 
Analisando os casos que encontramos dessa natureza, 
a comparacao da mensagem aparece no report, 
porem a discrepancia ocorre quando o teste nao mostra 
essa mensagem (passa por motivos de invalid input).
Eu classifiquei como message mismatch, 
mas creio que nesse caso seria invalid input.
}
